\documentclass[./Main.tex]{subfiles}
\begin{document}


\section{Licenses}
Our project will be licensed under GNU AGPLv3, some of the code/libraries used have individual licenses which will be summarised here.

\tocless\subsection{ANTLR}
Is licensed under the following BSD license, which is included in all files and/or subdirectories containing files covered by the license.



\tocless\subsection{Cassandra, Datastax, and cassandra-exporter-agent}
These three are licensed under the Apache license, version 2.0 (\href{https://www.apache.org/licenses/LICENSE-2.0}{https://www.apache.org/licenses/LICENSE-2.0}).


\tocless\subsection{BOOST}
Boost has its own license, which can be found \href{https://www.boost.org/users/license.html}{here.}


\tocless\subsubsection{ANTLR python3 and javascript grammar, curlcpp, and nlohmann-json}
These are covered by the MIT license, which is included in all files and/or subdirectories containing files covered by the license.



\tocless\subsection{curl}
Curl uses a custom license, which is included in all files and/or subdirectories containing files covered by the license. 



\tocless\subsection{RSA Data Security, Inc. MD5 Message-Digest
Algorithm}
For Md5 we use RSA Data Security, Inc. MD5 Message-Digest Algorithm, this has a license included in the files containing relevant code.



\tocless\subsection{Other things used by the project}
Our project also uses a number of other projects, our project does, however, not derive from these and their license does not have to be included.
SrcML is licensed under the GNU general public license, version 3. Git is licensed under the GNU general public license, version 2.0. Grafana is licensed under GNU general public license, version 3. Prometheus is licensed under Apache license, version 2.0.


\end{document}